Statically Typed String Sanitation Inside a Python (Technical Report)

### 2014-12-16 sanitation-psp14/tr/strings_chapter.tex
case and replace for p progress.

\item \textbf{Case PS-E-Concat}
Let $e = \rconcat{\rstr{s_1}}{\rstr{s_2}} \mapsto \rstr{s_1s_2}$. 
The only rule that applies is P-T-Concat, so $\theta \vdash e : \str$.
By canonical forms, $\theta \rstr{s_1s_2} : \str$.

\item \textbf{Case PS-E-CaseLeft}
Let $\iota = \strcase{\iota_1}{\iota_2}{x,y.\iota_3} \mapsto \strcase{\iota_1'}{\iota_2}{x,y.\iota_3}$
when $\iota_1 \mapsto \iota_1'$.
The only rule that applies is P-T-Case, so $\theta \vdash \iota : \tau$ where:
\begin{align*}
  \theta &\vdash \iota_1 : \str 
  \theta &\vdash \iota_2 : \tau
  \theta, x : \str, y : \str &\vdash \iota_3 : \tau
\end{align*}
By induction, $\theta \vdash \iota_1' : \str$.
By P-T-Case, $\thet \vdash \strcase{\iota_1}{\iota_2}{x,y.\iota_3} : \tau$.

\item \textbf{Case PS-E-CaseRight}
Let $\iota = \strcase{\iota_1}{\iota_2}{x,y.\iota_3} \mapsto \strcase{\iota_1}{\iota_2}{x,y.\iota_3}$
when $\iota_1 \mapsto \iota_1'$.
The only rule that applies is P-T-Case, so $\theta \vdash \iota : \tau$ where:
\begin{align*}
  \theta &\vdash \iota_1 : \str 
  \theta &\vdash \iota_2 : \tau
  \theta, x : \str, y : \str &\vdash \iota_3 : \tau
\end{align*}
By induction, $\theta \vdash \iota_1' : \str$.
By P-T-Case, $\thet \vdash \strcase{\iota_1}{\iota_2}{x,y.\iota_3} : \tau$.

>>>>

\item \textbf{Case PS-E-Concat}
Let $e = \rconcat{\rstr{s_1}}{\rstr{s_2}} \mapsto \rstr{s_1s_2}$. 
The only rule that applies is P-T-Concat, so $\emptyset \vdash e : \str$.
By canonical forms, $\emptyset \rstr{s_1s_2} : \str$.

\item \textbf{Case PS-E-CaseLeft}
Let $\iota = \strcase{\iota_1}{\iota_2}{x,y.\iota_3} \mapsto \strcase{\iota_1'}{\iota_2}{x,y.\iota_3}$
when $\iota_1 \mapsto \iota_1'$.
The only rule that applies is P-T-Case, so $\emptyset \vdash \iota : \tau$ where:
\begin{align*}
  \emptyset &\vdash \iota_1 : \str  \\
  \emptyset &\vdash \iota_2 : \tau \\
  \emptyset, x : \str, y : \str &\vdash \iota_3 : \tau 
\end{align*}
By induction, $\emptyset \vdash \iota_1' : \str$.
By P-T-Case, $\emptyset \vdash \strcase{\iota_1}{\iota_2}{x,y.\iota_3} : \tau$.

\item \textbf{Case PS-E-CaseEpsilon}
Let $\iota = \strcase{\rstr{\epsilon}}{\iota_2}{x,y.\iota_3} \mapsto \iota_2$.
The only rule that applies is P-T-Case, so $\emptyset \vdash \iota : \tau$ where
$\iota_2 : \tau$.

\item \textbf{Case PS-E-Case}
Let $\iota = \strcase{\rstr{as}}{\iota_2}{x,y.\iota_3} \mapsto [\rstr{a}, \rstr{s} / x,y] \iota_3$
The only rule that applies is P-T-Case, so $\emptyset \vdash \iota : \tau$ where:
\begin{align*}
  \emptyset &\vdash \iota_1 : \str \\
  \emptyset &\vdash \iota_2 : \tau \\
  \emptyset, x : \str, y : \str &\vdash \iota_3 : \tau
\end{align*}
The result follows by the substitution lemma.

\item \textbf{Case PS-E-ReplaceLeft}
Let $\iota = \rreplace{\iota_1}{\iota_2}{\iota_3} \mapsto \rreplace{\iota_1'}{\iota_2}{\iota_3}$
where $\iota_1 \mapsto \iota_1'$.
The applicable typing rule is P-T-Replace, so $\emptyset \vdash \iota : \str$ where:
\begin{align*}
  \emptyset &\vdash \iota_1 : \regex \\
  \emptyset &\vdash \iota_2 : \str \\
  \emptyset &\vdash \iota_3 : \str
\end{align*}

By induction, $\emptyset \vdash \iota_1' : \regex$.
Therefore, $\emptyset \vdash \rreplace{\iota_1'}{\iota_2}{\iota_3}$.

\item \textbf{Case PS-E-ReplaceMid}
Let $\iota = \rreplace{\iota_1}{\iota_2}{\iota_3} \mapsto \rreplace{\iota_1}{\iota_2'}{\iota_3}$
where $\iota_2 \mapsto \iota_2'$.
The applicable typing rule is P-T-Replace, so $\emptyset \vdash \iota : \str$ where:
\begin{align*}
  \emptyset &\vdash \iota_1 : \regex \\
  \emptyset &\vdash \iota_2 : \str \\
  \emptyset &\vdash \iota_3 : \str
\end{align*}

By induction, $\emptyset \vdash \iota_2' : \str$.
Therefore, $\emptyset \vdash \rreplace{\iota_1}{\iota_2'}{\iota_3}$.

\item \textbf{Case PS-E-ReplaceRight}
Let $\iota = \rreplace{\iota_1}{\iota_2}{\iota_3} \mapsto \rreplace{\iota_1}{\iota_2}{\iota_3'}$
where $\iota_3 \mapsto \iota_3'$.
The applicable typing rule is P-T-Replace, so $\emptyset \vdash \iota : \str$ where:
\begin{align*}
  \emptyset &\vdash \iota_1 : \regex \\
  \emptyset &\vdash \iota_2 : \str \\
  \emptyset &\vdash \iota_3 : \str
\end{align*}

By induction, $\emptyset \vdash \iota_3' : \str$.
Therefore, $\emptyset \vdash \rreplace{\iota_1}{\iota_2}{\iota_3'}$.

\item \textbf{Case PS-E-Replace}
Let $\iota = \rreplace{\rx{r}}{\rstr{s_2}}{\rstr{s_3}} \mapsto \rstr{\lreplace{r}{s_2}{s_3}}$.
The applicable typing rule is P-T-Replace, so $\emptyset \vdash \iota : \str$.
The result follows by canonical forms.
